checkData

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

```{r}
d_journals %>%
  group_by(journal) %>%
  summarise(num_unique_emp = n_distinct(anyPPC), unique_emp = toString(unique(anyPPC))) %>%
  filter(num_unique_prices > 1)

>>>>

```{r}
d_journals %>%
  group_by(journal) %>%
  summarise(unique_responses = n_distinct(anyPPC)) %>% # get the number of unique responses to this Q (should be 1 if they match)
  filter(unique_responses > 1)
